\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Assignment 6}

\author{Timothy Yong, Eric Bronner, Aedan Dispenza, Jason Davis}

\date{11/11/14}

\begin{document}
\maketitle

\bigskip

\noindent PROBLEM 1

\begin{enumerate}

\item[1.] Build a prefix tree out of the set of strings, $D$.  $O(n)$
\item[2.] Query prefix tree to find $S_1$ and $S_2$. $O(m)$ (Essentially, the tree runs in $<O(n), O(m)>$)
\item[3.] Compute $LCA(S_1,S_2)$. $<O(n), O(1)>$ 

\item[] This algorithm runs in $<O(n), O(m)>$, but can be reduced by hashing all leaf labels to $<O(n), O(1)>$.

\end{enumerate}

\bigskip
\bigskip

\noindent PROBLEM 2

\begin{enumerate}

\item[a.] Construct a tree out of the string such that palindromes are recursively defined, and all other substrings are just one node. The number of edges in a tree is $O(n)$ in respect to the length of the string, so there cannot be more than linear palindromes.

 \item[b.] Build a non-compressed suffix tree out of the string, and another of the reversed string. Take the intersection of these trees. Trim all branches that are not palindromes.  $<O(nm), O(m)>$

\end{enumerate}

\bigskip
\bigskip

\noindent PROBLEM 3

\begin{enumerate}

\item[]  Build a non-compressed suffix tree out of the string, and another of the reversed string. Take the intersection of these trees; whatever intersects is a palindrome. Use DFS to preprocess the depths of the substrings. $O(n)$

\end{enumerate}

\bigskip
\bigskip

\noindent PROBLEM 4

\begin{enumerate}

\item[]  Construct a compressed suffix tree $T$ out of $S$. Remove all leaf nodes and traverse the tree. Get the intersection between the tree returned from the algorithm from problem 2 and $T$, and store it in $U$. Subtract $U$ from $T$. The longest remaining substring is the longest repeated substring.

\end{enumerate}

\end{document}